FITS format for planetary surfaces: definitions, applications and best practices.

### 2018-01-24 epss_marmo.tex

\begin{table}
\label{table:proj}
\caption{Projection names and codes already available in FITS suitable for planetary applications:
their translation in PDS vocabulary is also provided}
\centering
\begin{tabular}{l l l}
\hline
FITS Name$^{a}$ & FITS code$^{a}$ & PDS name \\ 
\hline
Sanson-Flamsteed & SFL & \\
Zenithal Equal-Area & ZEA & \\
Conic ortomorphic & COO & \\
Plate Carre & CAR & \\
generalization of Lambert Equal-Area & CEA \\
Mercator & MER & \\
Ortographic & SIN & \\
Zenithal perspective & AZP & \\
Stereographic & STG & \\
\hline
\multicolumn{3}{l}{$^{a}$From \citet{calagreisenI}}
\end{tabular}
\end{table}

>>>>

\begin{table}
\label{table:proj}
\caption{Projection names and codes already available in FITS suitable for planetary applications:
their translation in PDS vocabulary is also provided}
\centering
\begin{tabular}{l l l}
\hline
FITS Name$^{a}$ & FITS code$^{a}$ & PDS name$^{b}$ \\ 
\hline
Sanson-Flamsteed & SFL & Sinusoidal \\
Zenithal Equal-Area & ZEA & Lambert Azimuthal Equal Area \\
Conic ortomorphic & COO & Lambert Conformal Conic\\
Plate Carre & CAR & Equirectangular \\
Cylindrical Equal-Area & CEA & \\
Mercator & MER & Mercator, Oblique Mercator \\
Ortographic & SIN & Orthographic \\
Zenithal perspective & AZP & \\
Stereographic & STG & \\
\hline
\multicolumn{3}{l}{$^{a}$From \citet{calagreisenI}} \\
\multicolumn{3}{l}{$^{b}$From the PDS4 Data Dictionary\footnote{https://pds.jpl.nasa.gov/pds4/doc/dd/current/PDS4\_PDS\_DD\_1900.pdf}}
\end{tabular}
\end{table}
